Comparative Analysis of the wav2vec 2.0 Feature Extractor

### 2023-03-07 main.tex
update AM text

\subsection{Acoustic Model}
The \gls{AM} mainly consists of \gls{VGG} \addref blocks for downsampling and 12 \conformer blocks.
The \gls{VGG} downsampling uses three 3x3-convolutional layers with 32, 64 and 64 channels, respectively.
In total, a subsampling factor of 4 in the time dimension is achieved by the strided convolutions so that the \conformer operates on frames with a shift of \SI{40}{\milli\second}.
The feature dimension is reduced by a factor of 2 due to max pooling and then multiplied by the number of channels in the last convolution resulting in a total increase by factor 32 in our case.
\draft{
There is a linear layer and dropout here.
The \conformer blocks should be described here.
}
The configuration follows the setup in \cite{zeineldeen2022robustconformer} \TODO{check!}.

>>>>

\subsection{Acoustic Model}
The \gls{AM} mainly consists of \gls{VGG} \addref blocks for downsampling and 12 \conformer blocks.
Its configuration mostly follows \cite{zeineldeen2022conformer} and \cite{zhou2022efficient}.
The \gls{VGG} downsampling uses three 3x3-convolutional layers with 32, 64 and 64 channels, respectively.
In total, a subsampling factor of 4 in the time dimension is achieved by the strided convolutions so that the \conformer operates on frames with a shift of \SI{40}{\milli\second}.
The feature dimension is reduced by a factor of 2 due to max pooling and then multiplied by the number of channels in the last convolution resulting in a total increase by factor 32 in our case.
After a linear projection to a 512-dimensional representation and dropout of 0.1, the 12 \conformer blocks with an inner dimension of 512, swapped convolution and multi-headed self-attention modules and 8 heads are applied.
